\documentclass[pdf]{beamer}
\mode<presentation>{}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}

\usetheme{Warsaw}
\usecolortheme{dolphin}

\title{Spin models on random bipartite graphs}
\author{Shane Harding \\ Supervisor: Mike Peardon}

\begin{document}


\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Project description}
In this project I will develop MPI software to run an Ising model simulation on a random bipartite graph.
\begin{itemize}
\item A bipartite graph is one where the vertices can be divided into two disjoint sets, $A$ and $B$, such that every edge connects a vertex in $A$ to one in $B$.
\item Then each vertext is given a spin, up or down. And the spins interact only with the others that it's connected to by an edge.
\item An investigation of the best way to partition a random graph into sub-domains to be handled on MPI cores will be carried out. 
\item The phase structure of these spin models will be studied in detail. The physical meaning will be analysed.
\end{itemize}
\end{frame}


\begin{frame}
\frametitle{Outline of plan}
\begin{itemize}
\item Write a general MPI code for the problem.
\item Specialise the code to look at specific cases. Could be graphs with unique or unusual properties that would make for some interesting parallelisation or physics.
\item Analyse performance aspects of the code.
\item Physical meaning of the interactions and the results of the simulations will be studied
\end{itemize}
\end{frame}



\end{document}
